---
title: "Election Forecasts"
output: html_document
---

<style>
paragraph {
    font-size: 19px;
  }
.paragraph2 {
    font-size: 21px;
  }
.header {
    font-family: Arial, Helvetica, sans-serif;
  }
</style>

```{r echo=FALSE, include=FALSE}
source("C:\\Users\\Elliott\\Desktop\\Random Analysis\\2016_election_analysis\\main.R")
```

<p class="header">
<center>
  <h1>Election Scenarios</h1>
</center>
</p>

<p class="paragraph2">
Suppose the voting of states with insufficient polling data mirrors that of previous election cycles:
</p>

<p class="paragraph">
Political Climate | Expected Result             | Victor
-------------     |   -------------             |------------- 
2000              |   `r outcome_2000_climate`  |`r margin2000`
2004              |   `r outcome_2004_climate`  |`r margin2004`
2008              |   `r outcome_2008_climate`  |`r margin2008`
2012              |   `r outcome_2012_climate`  |`r margin2012`
</p>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<center>
  <h1>Current Prediction Map</h1>
</center>

```{r map, echo=FALSE,fig.width=8,fig.align='center'}
gg
```

<center>
  <h1>State Forecasts</h1>
</center>

```{r stateplots, echo=FALSE,fig.align='center',fig.width=9, fig.height=9}
multiplot(plotlist = plots,cols=3)
```
